Pitfall of Prediction-orienterd Machine Learning Methods and Economic Value of Statistical Efficiency in On-farm Precision Experimentation

### 2022-02-26 Writing/manuscript.rmd
codes to generate pairwise t-test updated

@@

# Tables {-}

```{r count-table, echo=FALSE, cache=FALSE}
prt_table <- est_data %>% 
    .[order(sim, model), ] %>% 
    .[, y := (rmse_cv==min(rmse_cv)) %>% as.numeric(), by = .(sim, field_size)] %>% 
    .[, eonr := (rmse_eonr==min(rmse_eonr)) %>% as.numeric(), by = .(sim, field_size)] %>% 
    .[, pi := (profit==max(profit)) %>% as.numeric(), by = .(sim, field_size)] %>% 
    .[, .(`yield` = (sum(y)/.N*100) %>% round(2),
          `EONR` = (sum(eonr)/.N*100) %>% round(2),
          `profit` = (sum(pi)/.N*100) %>% round(2)), by = .(field_size, model)]
# datasummary(
#         field_size * (yield + EONR + profit) ~ factor(model) * (Mean), 
#         data = count_table,
#         title = 'Percentage (%) of each model being the best-performing among the five models in a single simulation round',
#         notes = c('A note at the bottom of the table.')
#     )
count_table <- prt_table %>% 
    #=== Wide to Long: melt()
    melt(id.vars = c('field_size','model')) %>% 
    #=== Long to Wide: dcast()
    dcast(field_size + variable ~ model, value.var = "value")
knitr::kable(count_table, format = "markdown",
             caption = "Percentage (%) of each model being the best-performing among the five models in a single simulation round")
```

```{r pair-table-yield, echo=FALSE, cache=FALSE}
model_list <- unique(est_data$model) %>% .[order(.)] %>% as.character()
pair_df <- data.frame()
for(i in 1:length(model_list)){
    for(j in 1:length(model_list)){
        pi <- est_data %>% 
            filter(field_size=="37.3 ha", model==model_list[i]) %>% 
            pull(rmse_cv)
        pj <- est_data %>% 
            filter(field_size=="37.3 ha", model==model_list[j]) %>% 
            pull(rmse_cv)
        pv <- t.test(pi, 
                     pj, 
                     paired = TRUE)

        pair_df[model_list[i], model_list[j]] <- 
            round(pv$estimate, 2)
        pair_df[as.character(i), model_list[j]] <- 
            paste0("(", round(pv$p.value, 3), ")")
    }
}
pair_df[is.na(pair_df)] <- ""
knitr::kable(pair_df, format = "markdown",
             caption = "Pairwise t-test of predicted yield RMSE between models, Large field (37.3 ha), values are the difference in RMSE (row vs. index) (kg/ha), p-values in parenthese")
```

```{r pair-table-eonr, echo=FALSE, cache=FALSE}
model_list <- unique(est_data$model) %>% .[order(.)] %>% as.character()
pair_df <- data.frame()
for(i in 1:length(model_list)){
    for(j in 1:length(model_list)){
        pi <- est_data %>% 
            filter(field_size=="37.3 ha", model==model_list[i]) %>% 
            pull(rmse_eonr)
        pj <- est_data %>% 
            filter(field_size=="37.3 ha", model==model_list[j]) %>% 
            pull(rmse_eonr)
        pv <- t.test(pi, 
                     pj, 
                     paired = TRUE)

        pair_df[model_list[i], model_list[j]] <- 
            round(pv$estimate, 2)
        pair_df[as.character(i), model_list[j]] <- 
            paste0("(", round(pv$p.value, 3), ")")
    }
}
pair_df[is.na(pair_df)] <- ""
knitr::kable(pair_df, format = "markdown",
             caption = "Pairwise t-test of predicted EONR RMSE between models, Large field (37.3 ha), values are the difference in RMSE (row vs. index) (kg/ha), p-values in parenthese")
```

```{r pair-table-profit, echo=FALSE, cache=FALSE}
model_list <- unique(est_data$model) %>% .[order(.)] %>% as.character()
pair_df <- data.frame()
for(i in 1:length(model_list)){
    for(j in 1:length(model_list)){
        pi <- est_data %>% 
            filter(field_size=="37.3 ha", model==model_list[i]) %>% 
            pull(profit)
        pj <- est_data %>% 
            filter(field_size=="37.3 ha", model==model_list[j]) %>% 
            pull(profit)
        pv <- t.test(pi, 
                     pj, 
                     paired = TRUE)

        pair_df[model_list[i], model_list[j]] <- 
            round(pv$estimate, 2)
        pair_df[as.character(i), model_list[j]] <- 
            paste0("(", round(pv$p.value, 3), ")")
    }
}
pair_df[is.na(pair_df)] <- ""
knitr::kable(pair_df, format = "markdown",
             caption = "Pairwise t-test of profits between models, Large field (37.3 ha), values are the difference in profits (row vs. index) (kg/ha), p-values in parenthese")
```

>>>>

<div id="refs"></div>

@@

# Appendix {-}

```{r, child = "appendix.Rmd"}
```
